Circumpolar variations in the chaotic nature of Southern Ocean eddy dynamics

### 2022-01-06 paper/main.tex
altering description of delayed timescale

Averaged over the entire Southern Ocean two significant timescales of correlation are found between wind stress and the ensemble mean EKE: one at 4-6 months, and the other at $\sim$30 months.
The rapid timescale is the expected Ekman response, in which wind stress tilts isopycnals to store available potential energy, which is then released to EKE through baroclinic instability \citep[e.g.][]{Sinha2016}.
The slower timescale is similar to that proposed by \citet{Meredith-Hogg-2006}, based on the single large Southern Ocean wind event in 1999.
This timescale is consistent with the  topographic feedback mechanism of \citet{Hogg-Blundell-2006}, in which a delayed amplification of the EKE response can occur through the topographic steering of currents away from the zonal direction, which decreases the stability of the current.

>>>>

Averaged over the entire Southern Ocean two significant timescales of correlation are found between wind stress and the ensemble mean EKE: one at 4-6 months, and the other at $\sim$30 months.
The rapid timescale is the expected Ekman response, in which wind stress tilts isopycnals to store available potential energy, which is then released to EKE through baroclinic instability \citep[e.g.][]{Sinha2016}.
This mechanism the direct eddy response to wind stress changes via baroclinic instability.

The slower timescale is similar to that proposed by \citet{Meredith-Hogg-2006}, based on a single large Southern Ocean wind event in 1999.
This timescale is consistent with the  topographic feedback mechanism of \citet{Hogg-Blundell-2006}.
Under this mechanism, the system first responds directly, via baroclinic instability, as described above. 
The stronger eddy field acts to increase the vertical momentum transfer which enables topography to steer the current and thereby increase the meridional component of the mean flow. 
Currents with a non-zonal component are more susceptible to baroclinic instability which thus produces a delayed amplification of the EKE response.
This mechanism describes a positive feedback between the eddy field and the mean currents which acts to enhance EKE over longer timescales.
